---
title: "portfolio"
author: "Joy Oduor"
date: "2024-02-21"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
---
```{r setup, include=FALSE}
library(tidyverse)
library(spotifyr)
library(compmus)
library(ggplot2)
library(compmus)
```

### Home

Welcome, Please bare with me. 

- Corpus Albums (100 Songs)
  
  Nostalgia (2015) - Chase Atlantic (5 Songs)
  
  Chase Atlantic (2017) - Chase Atlantic (14 Songs)
  
  Channel Orange (2012) - Frank Ocean (17 Songs)
  
  Blonde (2016) - Frank Ocean (17 Songs)
  
  Collide with the sky (2012) - pierce the veil (12 Songs)
  
  Dead (2015) - Blackbear (5 songs)
  
  Into (2017) - Sonder (7 Songs)
  
  SYRE (2017)- Jaden (17 Songs)
  
  Freudian (2017) - Daniel Caesar  (10 Songs)

***

### Week 1/7: Fourier Analysis - Data Visualisation - Chase Atlantic 

```{r playlist audio features}
corpus<- get_playlist_audio_features("", "4rAgX03HCHgKDTEpwCOzKG")
corpus_nostalgia <- get_playlist_audio_features("", "6W3I5rQT7GUuaamQwgX3PL")
corpus_collidewiththesky <- get_playlist_audio_features("","45MgDPngswNvw54lk3gYoF")
corpus_channelorange <- get_playlist_audio_features("", "3yoSA3ffnSdAifk1a8T9SM")
corpus_dead <- get_playlist_audio_features("", "5AlLcKu3I0LNrN4xCJ3oqN")
corpus_chaseatlantic <- get_playlist_audio_features("", "1TM6VvzBZ8p0gqelKulqFf")
corpus_syre <- get_playlist_audio_features("", "4tBQbGu9Zo8R35NlxtheuZ")
corpus_into <- get_playlist_audio_features("", "74kfEsw9YeK6dXbCUg5cwd")
corpus_freudian <- get_playlist_audio_features("", "6bDoKNaOQT1xvfbtktLpJB")
corpus_blonde <- get_playlist_audio_features("", "6S7fG76Xd2q1Z20eQjqAiu")
```
```{r W7 Chase Atlantic Data Visualisations}
chase_atlantic <-
  bind_rows(
    corpus_nostalgia |> mutate(category = "corpus_nostalgia"),
    corpus_chaseatlantic |> mutate(category = "corpus_chaseatlantic")
  )
chase_atlantic |>
  ggplot(aes(x = energy)) +
  geom_histogram(binwidth = 0.1) +
  facet_wrap(~category)
chase_atlantic |>
  ggplot(aes(x = category, y = energy)) +
  geom_violin()
chase_atlantic |> ggplot(aes(x = valence, y = energy)) + geom_point() + geom_smooth()
```

***
### Week 1/7: ggplot - Data Visualisation - Chase Atlantic 

```{r W7 Chase Atlantic Graph}
chase_atlantic |>                  
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) |>
  ggplot(                     
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = mode
    )
  ) +
  geom_point() +              
  geom_rug(linewidth = 0.1) + 
  geom_text(                  
    aes(
      x = valence,
      y = energy,
      label = label
    ),
    data = 
      tibble(
        label = c("Nostalgia", "Chase Atlantic"),
        category = c("corpus_nostalgia", "corpus_chaseatlantic"),
        valence = c(0.104, 0.0339),
        energy = c(0.992, 0.00166)
      ),
    colour = "black",         
    size = 3,                 
    hjust = "left",           
    vjust = "center",         
    nudge_x = 0.03            
  ) +
  facet_wrap(~ category) +    
  scale_x_continuous(         
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),  
    minor_breaks = NULL       
  ) +
  scale_y_continuous(         
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        
    type = "qual",            
    palette = "Paired"        
  ) +
  scale_size_continuous(      
    trans = "exp",            
    guide = "none"            
  ) +
  theme_light() +             
  labs(                       
    x = "Valence",
    y = "Energy",
    colour = "Mode"
  )
```

***

### Week 1/7: Fourier Analysis - Data Visualisation - Frank Ocean

```{r W7 Frank Ocean Data Visualisations}
frank_ocean <-
  bind_rows(
    corpus_channelorange |> mutate(category = "corpus_channelorange"),
    corpus_blonde |> mutate(category = "corpus_blonde")
  )
frank_ocean |>
  ggplot(aes(x = energy)) +
  geom_histogram(binwidth = 0.1) +
  facet_wrap(~category)
frank_ocean |>
  ggplot(aes(x = category, y = energy)) +
  geom_violin()
frank_ocean |> ggplot(aes(x = valence, y = energy)) + geom_point() + geom_smooth()
```

***

### Week 1/7: ggplot - Data Visualisation - Frank Ocean

```{r W7 Frank Ocean Graph}
frank_ocean |>                  
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) |>
  ggplot(                     
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = mode
    )
  ) +
  geom_point() +              
  geom_rug(linewidth = 0.1) + 
  geom_text(                  
    aes(
      x = valence,
      y = energy,
      label = label
    ),
    data = 
      tibble(
        label = c("channel Orange", "Blonde"),
        category = c("corpus_channelorange", "corpus_blonde"),
        valence = c(0.104, 0.0339),
        energy = c(0.992, 0.00166)
      ),
    colour = "black",         
    size = 3,                 
    hjust = "left",           
    vjust = "center",         
    nudge_x = 0.03            
  ) +
  facet_wrap(~ category) +    
  scale_x_continuous(         
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),  
    minor_breaks = NULL       
  ) +
  scale_y_continuous(         
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        
    type = "qual",            
    palette = "Paired"        
  ) +
  scale_size_continuous(      
    trans = "exp",            
    guide = "none"            
  ) +
  theme_light() +             
  labs(                       
    x = "Valence",
    y = "Energy",
    colour = "Mode"
  )
```

***

### Week 2/8 - Chromagrams - Pierce the Veil

```{r W2 Hell Above}
hell_above <-
  get_tidy_audio_analysis("3EKh7JNsBrGoh2xqPotBKT") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
```
```{r W2 Hell Above Chromagram}
hell_above |>
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) |>
  compmus_gather_chroma() |> 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```

***

### Week 2/8 - Dynamic warping - Pierce the Veil

```{r W2 Match into water, King for a day}
a_match_into_water <-
  get_tidy_audio_analysis("54MXF9I8s3DuiQo3g0gZ5k") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
  
king_for_a_day <-
  get_tidy_audio_analysis("1IT0WQk5J8NsaeII8ktdlZ") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)
```

```{r W2 Dynamic warping}
compmus_long_distance(
	a_match_into_water |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
	king_for_a_day |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "A Match Into Water", y = "King for a day") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
```

***

